DOpElib:\\ Differential Equations and Optimization Environment

### 2017-04-12 Examples/Documentation/examples.tex

\section{Creating new examples}
\label{getting_started}
Before being able to change and compile the new code, the user must 
follow some easy steps in order to modify the information related to the old code. In 
this section we explain how to modify such information using as model 
\texttt{PDE/StatPDE/Example1}.

\begin{enumerate}
 \item In a first step, we copy \texttt{Example1} and renamed it, e.g., 
\texttt{MyWonderfulFirstExample}. At the same time it is important to remove the repository 
information that it is stored in the directory \texttt{.svn/}. \\
After having reached the folder of the example in question in the terminal, 
\texttt{PDE/StatPDE} in our case, we perform these operation writing the following:
\begin{verbatim}
cp -r Example1 MyWonderfulFirstExample
cd MyWonderfulFirstExample
rm -rf .svn
cd Test
rm -rf .svn
\end{verbatim}
Please note that removing the \texttt{.svn} sub-directories is important,
as otherwise your files may be replaced or changed during your next
update. Also, if you can submit information to the subversion repository 
you might accidentally overwrite the original example, here \texttt{Example1}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Changing from Release mode to Debug mode}
In a specific example go into the autobuild folder 
and change therein:
\begin{lstlisting}
CMAKE_BUILD_TYPE:STRING=Release
\end{lstlisting}
to 
\begin{lstlisting}
Debug Release RelWithDebInfo MinSizeRel
\end{lstlisting}
Then go one folder back and type as usual `make' to build the executable file.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Creating new examples}
\label{getting_started}
Before being able to change and compile the new code, the user must 
follow some easy steps in order to modify the information related to the old code. In 
this section we explain how to modify such information using as model 
\texttt{PDE/StatPDE/Example1}.

\begin{enumerate}
\item \textbf{New: in git from March 2017} In a first step, we copy \texttt{Example1} and renamed it, e.g., 
\texttt{MyWonderfulFirstExample}. 
After having reached the folder of the example in question in the terminal, 
\texttt{PDE/StatPDE} in our case, we perform these operation writing the following:
\begin{verbatim}
cp -r Example1 MyWonderfulFirstExample
cd MyWonderfulFirstExample
\end{verbatim}

 \item \textbf{Old: in the svn up to version 8.3} In a first step, we copy \texttt{Example1} and renamed it, e.g., 
\texttt{MyWonderfulFirstExample}. At the same time it is important to remove the repository 
information that it is stored in the directory \texttt{.svn/}. \\
After having reached the folder of the example in question in the terminal, 
\texttt{PDE/StatPDE} in our case, we perform these operation writing the following:
\begin{verbatim}
cp -r Example1 MyWonderfulFirstExample
cd MyWonderfulFirstExample
rm -rf .svn
cd Test
rm -rf .svn
\end{verbatim}
Please note that removing the \texttt{.svn} sub-directories is important,
as otherwise your files may be replaced or changed during your next
update. Also, if you can submit information to the subversion repository 
you might accidentally overwrite the original example, here \texttt{Example1}.
